working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-22 Manuscript_draft/Manuscript_draft.Rmd
small change

Pollinator sharing can have negative consequences for plant fitness with the arrival of foreign pollen. However, the costs of heterospecific pollen are not yet well understood. We conducted a glasshouse experiment to understand how phylogenetic relatedness and plant traits mediate the impacts of heterospecific pollen transfer. We conducted 4XXXX crosses by experimentally transferring pollen (50% and 100% ratio) with reciporcal crosses between 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae. Seed set was used as proxy of plant fitness. We found that for 65% of the treatments with 50% mix reduced seed set. Moreover, the reduction in seed set was dependent on the degree of relatedness and reproductive traits of the pollen recipient and not the pollen donor. Our results show that certain traits, particularly compatibility system, are critical in understanding the costs of heterospecific pollen.
\vspace{3mm}\hrule

>>>>

Pollinator sharing can have negative consequences for plant fitness with the arrival of foreign pollen. However, the costs of heterospecific pollen are not yet well understood. We conducted a glasshouse experiment to understand how phylogenetic relatedness and plant traits mediate the impacts of heterospecific pollen transfer. We conducted 1800 crosses by experimentally transferring pollen (50% and 100% ratio) with reciporcal crosses between 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae. Seed set was used as proxy of plant fitness. We found that for 65% of the treatments with 50% mix reduced seed set. Moreover, the reduction in seed set was dependent on the degree of relatedness and reproductive traits of the pollen recipient and not the pollen donor. Our results show that certain traits, particularly compatibility system, are critical in understanding the costs of heterospecific pollen.
\vspace{3mm}\hrule

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
small change

Pollinator sharing can have negative consequences for plant fitness with
the arrival of foreign pollen. However, the costs of heterospecific
pollen are not yet well understood. We conducted a glasshouse experiment
to understand how phylogenetic relatedness and plant traits mediate the
impacts of heterospecific pollen transfer. We conducted 4XXXX crosses by
experimentally transferring pollen (50\% and 100\% ratio) with
reciporcal crosses between 10 species belonging to three different
families: Brassicaceae, Solanaceae and Convolvulaceae. Seed set was used
as proxy of plant fitness. We found that for 65\% of the treatments with
50\% mix reduced seed set. Moreover, the reduction in seed set was
dependent on the degree of relatedness and reproductive traits of the
pollen recipient and not the pollen donor. Our results show that certain
traits, particularly compatibility system, are critical in understanding
the costs of heterospecific pollen. \vspace{3mm}\hrule

>>>>

Pollinator sharing can have negative consequences for plant fitness with
the arrival of foreign pollen. However, the costs of heterospecific
pollen are not yet well understood. We conducted a glasshouse experiment
to understand how phylogenetic relatedness and plant traits mediate the
impacts of heterospecific pollen transfer. We conducted 1800 crosses by
experimentally transferring pollen (50\% and 100\% ratio) with
reciporcal crosses between 10 species belonging to three different
families: Brassicaceae, Solanaceae and Convolvulaceae. Seed set was used
as proxy of plant fitness. We found that for 65\% of the treatments with
50\% mix reduced seed set. Moreover, the reduction in seed set was
dependent on the degree of relatedness and reproductive traits of the
pollen recipient and not the pollen donor. Our results show that certain
traits, particularly compatibility system, are critical in understanding
the costs of heterospecific pollen. \vspace{3mm}\hrule
